\section*{Structure of the paper}
\begin{enumerate}
    \item Abstract
    \item Introduction (Ilias)
    \item Penalized Regression (Ilias)
    \begin{enumerate}
        \item Motivation for penalized regression: Find a data set where normal regression fails ($n \approx p$ or even $n < p$).
        \item Introduce Ridge regression, explain and apply to data set
        \item Introduce Lasso, explain and apply to (preferably the same) data set
        \item Possibly explain some other methods (like subset selection)
    \end{enumerate}
    \item Cross-validation and parameter selection (Nina)
    \begin{enumerate}
        \item Motivate importance of parameter selection and need for method of comparing different parameters
        \item Introduce cross-validation
    \end{enumerate}
    \item Comparison of Ridge and Lasso --> adhv epicurious dataset.
    \begin{enumerate}
        \item 700 predictors is not easy to interpret. Running Lasso on the data set will eliminate a lot of variables.
        \item Set the tag for '$22$-minute meals' of all dished that have high rating to $1$ and run Lasso. It should select that predictor.
        \item Restricting the data set to its first 700 rows makes $n \approx p$. Running Ridge on the data set will (hopefully) give better test errors than regular regression
        \item Which regression methods has the lowest test error? 
        \item Possibility to test multiple types of CV (although $k$-fold CV is best so maybe just use that?)
        \item Fun questions:
        \begin{itemize}
            \item What ingredients should we mix to get the highest rating?
            \item What are the proportions of nutritional values that get would get us the highest rating?
        \end{itemize}
    \end{enumerate}
    \item Conclusion (Nina)
    \begin{itemize}
        \item Write something about SCAD?
        \item Write something about LAR?
        \item Write something about where this is used?
        \item Summarize our findings?
        \item Compare our own implementation of Ridge and Lasso to the one in the R-package?
    \end{itemize}
\end{enumerate}